Contracts for Contracts

### 2023-07-11 paper/case_study.tex
fix broken url

\begin{table}
	\centering
	\begin{tabular}{cccc}
		\toprule
		\textbf{Type} & \textbf{Case} & \textbf{Date} & \textbf{Loss} \\
		\midrule
		\multirow{4}{*}{\rotatebox[origin=c]{90}{\begin{tabular}{@{}c@{}}Readonly \\Reentrancy\end{tabular}}} 
		& \href{https://medium.com/coinmonks/theoretical-practical-balancer-and-read-only-reentrancy-part-1-d6a21792066c}{Sentiment} & 04/05/23 & \$1M \\
		& \href{https://twitter.com/BlockSecTeam/status/1623901011680333824
		}{dForce} & 02/10/23 & \$3.65M \\
		& \href{https://twitter.com/peckshield/status/1614774855999844352}{MidasCapital} & 01/16/23 & \$650K \\ 
		& \href{https://quillaudits.medium.com/decoding-220k-read-only-reentrancy-exploit-quillaudits-30871d728ad5}{Market.xyz} & 10/24/22 & \$220K \\

@@

		\multirow{5}{*}{\rotatebox[origin=c]{90}{\begin{tabular}{@{}c@{}}Return Value\\Not Check\end{tabular}}} 
		& & & \\
		& & & \\
		& \href{https://medium.com/@QubitFin/protocol-exploit-report-305c34540fa3}{Qubit} & 01/28/22 & \$80M \\
		& & & \\
		& & & \\
		\bottomrule
	\end{tabular}
	\caption{Summary of case studies.}
	\label{tab:case}
\end{table}

>>>>

\begin{table}
	\centering
	\begin{tabular}{cccc}
		\toprule
		\textbf{Type} & \textbf{Case} & \textbf{Date} & \textbf{Loss} \\
		\midrule
		\multirow{4}{*}{\rotatebox[origin=c]{90}{\begin{tabular}{@{}c@{}}Readonly \\Reentrancy\end{tabular}}}
		& \href{https://medium.com/coinmonks/theoretical-practical-balancer-and-read-only-reentrancy-part-1-d6a21792066c}{Sentiment} & 04/05/23 & \$1M \\
		& \href{https://twitter.com/peckshield/status/1623910257033617408} %\href{https://twitter.com/BlockSecTeam/status/1623901011680333824
		{dForce} & 02/10/23 & \$3.65M \\
		& \href{https://twitter.com/peckshield/status/1614774855999844352}{MidasCapital} & 01/16/23 & \$650K \\
		& \href{https://quillaudits.medium.com/decoding-220k-read-only-reentrancy-exploit-quillaudits-30871d728ad5}{Market.xyz} & 10/24/22 & \$220K \\

@@

		\multirow{5}{*}{\rotatebox[origin=c]{90}{\begin{tabular}{@{}c@{}}Return Value\\Not Check\end{tabular}}}
		& & & \\
		& & & \\
		& \href{https://medium.com/@QubitFin/protocol-exploit-report-305c34540fa3}{Qubit} & 01/28/22 & \$80M \\
		& & & \\
		& & & \\
		\bottomrule
	\end{tabular}
	\caption{Summary of case studies.\wac{The dForce link is broken. I changed it.}}
	\label{tab:case}
\end{table}
